Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-13 paper/paper.tex
Confusion about k=3

\begin{lemma}
  Every repartition of \TAlg has the cost $O(1)$.
\end{lemma}

\begin{theorem}
  In a single phase, \TAlg pays $O(\ell)$.
\end{theorem}

\begin{theorem}
  \TAlg is $O(\ell)$-competitive.
\end{theorem}
\begin{proof}
  OPT pays at least $1$ in a single phase.
\end{proof}

>>>>

\maciek{Define "component-respecting" algorithm}

\begin{lemma}
  \label{lem:1req}
  Serving each request incurs the cost at most $3\cdot\alpha$ for \TAlg.
\end{lemma}

\begin{proof}
  If no partition of \TAlg's components exist, then it performs no repartition, and it pays nothing.
  Hence, in the following we bound the cost of moving to component-respecting partition.

    Consider a request $(u, v)$ and let $U, V$ be clusters of these nodes.
    If $U=V$, then the request does not require a reconfiguration and GREEDY incurs no cost.
    Otherwise, we consider cases upon the type of clusters $U$ and $V$.
    Note that this is impossible that either $U$ or $V$ is $C_3$ as otherwise we encounter a component of size $4$ and this would contradict the case assumption that the component-respecting partition exists.
    If either $U$ or $V$ is $C_1$, then either cluster can fit the merged component, and the rebalance is local within $U$ and $V$, for the cost of at most $3$ migrations.

    Finally, we consider the case where both $U$ and $V$ are $C_2$. Note that $(u,v)$ cannot both belong to a component of size $2$, as this would mean that \TAlg has the component of size $4$, a contradiction with the case assumption that the component-respecting partition exists. 
    If either $u$ or $v$ belongs to a component of size $2$ then it suffices to exchange components of size $1$ between $U$ and $V$.
    Finally, if $u$ and $v$ belong to components of size $1$, then we must place them in a cluster different from $U$ and $V$.
    Note that in such case, a $C_1$-type cluster $W$ exists, as otherwise the input graph would not have a perfect partition. In this case GREEDY exchanges the nodes $u$ and $v$ with any two nodes of $W$, for the total cost of $2\cdot \alpha$.
\end{proof}

\begin{theorem}
  \TAlg is $O(\ell)$-competitive.
\end{theorem}
\begin{proof}
  Consider a request $(u,v)$.
  If $u$ and $v$ are collocated in the same server, then \TAlg pays nothing.

  \TAlg collocates nodes belonging to one component, hence during a single phase, we have at most $2\cdot \ell$ requests to non-collocated nodes.
  We use Lemma~\ref{lem:1req} to bound the cost of each such request, and therefore \TAlg pays $6\cdot\alpha\cdot \ell$ in a single phase.
  On the other hand, during each phase, OPT pays at least $1$.
\end{proof}
